---
title: ""
output: html_document
params:
  riskID: Preliminary Design
  projID: Biscayne Bay Coastal Wetlands (BBCW)
  p2ID: 	113846
  shinyrend: FALSE
---

```{css, echo=FALSE}
h1 {
  text-align: center;
}
```

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(readr) 
library(magrittr) 
library(dplyr) 
library(kableExtra) 
library(rlang)
library(plotly)
library(ggplot2)
library(ggrepel)
library(dplyr)
library(knitr)
library(crosstalk)
library(tidyverse)
library(english)
library(DT)
library(webshot)
library(erarr)
options(scipen = 999)
erisk_item <- readr::read_csv("../data/RISKLIST_FULL.csv")
risk_item_db<-data.frame(erisk_item)
erisk_project <- readr::read_csv("../data/PROJECTLIST_FULL.csv")
risk_project_db<-data.frame(erisk_project)
risk_treat <- readr::read_csv("../data/RISKTREATMENTLIST_FULL.csv",col_names = TRUE)
checkimagepath<-"../www/check.png"
erisk_item <- readr::read_csv("../data/RISKLIST_FULL.csv")
risk_item_db<-data.frame(erisk_item)
milestonedf<-read.csv("../data/PHASEMILESTONE.csv")
milestone_df<-data.frame(milestonedf)

risk_transact <- read_csv("../data/RISKTRANSACTIONLIST_FULL.csv")

erisk_ItemProj<-left_join(risk_item_db, risk_project_db, by = "PROJECT_ID")                                                                                                                          
risk_item_filt<- risk_item_db |>
  select(RISK_ID, PROJECT_ID, RISK_NAME , PROJECT_NAME, P2_NUMBER)



RiskImpactTable<-erisk_ItemProj |>
  select("RISK_ID","RISK_IDENTIFIER","P2_NUMBER.x", "PROJECT_ID","PROJECT_NAME.x", "RISK_NAME","RISKCATEGORY", "DISCIPLINE", "RISK_STATEMENT","LIKELIHOOD_DESC", "PROB_OCCURRENCE_EVIDENCE",  "COST_IMPACT_LOWEST", "COST_IMPACT_MOSTLIKELY", "COST_IMPACT_HIGHEST", "COST_IMPACT_EVIDENCE","SCHEDULE_IMPACT_LOWEST", "SCHEDULE_IMPACT_MOSTLIKELY", "SCHEDULE_IMPACT_HIGHEST", "SCHEDULE_IMPACT_EVIDENCE", "LIFECYCLEPHASENAME.x", "PERFORMANCEIMPACT_DESC", "PERFORMANCEIMPACT" ,"PROJECTPHASEID", "MILESTONE", "RISK_MANAGER", "COST_IMPACT_DISTTYPE", "SCHEDULE_IMPACT_DISTTYPE", "NO_PERFORMANCE_IMPACT", "NO_COST_IMPACT","NO_SCHEDULE_IMPACT")

risk_transact<-left_join(risk_transact, risk_item_filt, by=c("PROJECT_ID", "RISK_ID"))     
risk_treat<-left_join(risk_treat, risk_item_filt, by=c("PROJECT_ID", "RISK_ID"))



```

```{r echo=FALSE}
if (params$shinyrend)
  shiny::setProgress(0.25)  # set progress to 25%
```

```{r echo=FALSE, eval = params$projID != ""}
risk_item<-filter(RiskImpactTable, RiskImpactTable$RISK_NAME == params$riskID, RiskImpactTable$PROJECT_NAME.x == params$projID)
risk_treatment<-filter(risk_treat, risk_treat$PROJECT_NAME == params$projID, risk_treat$RISK_NAME == params$riskID)

```

      
```{r echo=FALSE, eval = params$p2ID != ""}
risk_item<-filter(RiskImpactTable, RiskImpactTable$RISK_NAME == params$riskID, RiskImpactTable$P2_NUMBER == params$p2ID)
risk_treatment<-filter(risk_treat, risk_treat$PROJECT_NAME == params$projID, risk_treat$RISK_NAME == params$riskID)

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
risk_item_table<- risk_item |>
  select(COST_IMPACT_LOWEST,COST_IMPACT_HIGHEST, COST_IMPACT_EVIDENCE,SCHEDULE_IMPACT_LOWEST, SCHEDULE_IMPACT_HIGHEST, SCHEDULE_IMPACT_EVIDENCE,PERFORMANCEIMPACT_DESC, PERFORMANCEIMPACT, PERFORMANCEIMPACT_DESC, SCHEDULE_IMPACT_DISTTYPE)


risk_treat_table<-risk_treatment |>
  select(RISK_TREATMENT_ID,PROPOSED_RISK_TREATMENT,COST_IMPACT_RISK_TREATMENT,
         SCHEDULE_IMPACT_RISK_TREATMENT, IMPLEMENTED, RISK_NAME) |>
  mutate(IMPLEMENT_IMG = case_when(
    IMPLEMENTED == 1 ~ checkimagepath,
    IMPLEMENTED == 0 ~ " ")) |>
  select(RISK_TREATMENT_ID,PROPOSED_RISK_TREATMENT,COST_IMPACT_RISK_TREATMENT,
         SCHEDULE_IMPACT_RISK_TREATMENT, IMPLEMENT_IMG) |>
  mutate(PROPOSED_RISK_TREATMENT = paste0(( "Measure "), str_to_title(english::english(RISK_TREATMENT_ID)),": ",PROPOSED_RISK_TREATMENT )) |>
  mutate(SCHEDULE_IMPACT_RISK_TREATMENT = paste(SCHEDULE_IMPACT_RISK_TREATMENT, "Days"))

treat_condit <- ifelse(nrow(risk_treat_table)>0,TRUE,FALSE)

  
```


#### Project: `r risk_item$PROJECT_NAME.x`

#### Risk Phase: `r risk_item$LIFECYCLEPHASENAME`, Category: `r risk_item$RISKCATEGORY`

# Risk Summary: `r risk_item$RISK_NAME`



```{r milestoneplot, fig.align='center', fig.height=2, fig.width=9, echo=FALSE}
erarr::milestoneplot(riskitem=risk_item, milestonedf = milestone_df)

```

```{r echo=FALSE}
if (params$shinyrend)
  shiny::setProgress(0.50)  # set progress to 50%
```


##### **Lead Discipline:** `r risk_item$DISCIPLINE`

##### `r risk_item$RISK_STATEMENT`


<center>
```{r echo=F, out.width="75%", fig.height=2}
monteframe<-data.frame(Opportunity=c(100), Low=c(100))
plot_ly()|>
  add_pie(monteframe$Opportunity, value=monteframe$Opportunity,title="Opportunity", textinfo='none',domain = list(row = 0, column = 0),hole = 0.7, marker = list(
        colors= "#1F78B4"))|>
  add_pie(monteframe$Opportunity, value=monteframe$Opportunity,title="Opportunity",textinfo='none',domain = list(row = 0, column = 1),hole = 0.7,marker = list(
        colors= "#1F78B4"))|>
  add_pie(monteframe$Low, value=monteframe$Low,title="Low",textinfo='none',domain = list(row = 0, column = 2),hole = 0.7,marker = list(
        colors= "#33A02C")) |>
    layout(title = "", showlegend = F,
                      grid=list(rows=1, columns=3),
    annotations = list(x = c(0.125,0.49, 0.9,0.12,0.485),
                            y = c(1.2, 1.2, 1.2,-0.15, -0.15),
                            text = c("Cost","Schedule","Performance","Mean: $0", "Mean: 0 Days"),
                            xref = "paper",
                            yref = "paper",
                            showarrow = F
                          ))


```
</center>

```{r echo=FALSE}
if (params$shinyrend)
  shiny::setProgress(0.75)  # set progress to 75%
```



#### **Event Likelihood:** `r risk_item$LIKELIHOOD_DISC`

#### `r risk_item$PROB_OCCURRENCE_EVIDENCE`


#### **No Impact**

| Cost Impact                 | Schedule Impact                   | Performance Impact                   |
|---------------------|-------------------------|---------------------------|
| No Cost Impact anticipated. | No Schedule Impact is Anticipated | No Performance Impact is anticipated |

#### **Uniform Example**

| Cost Impact                                   | Schedule Impact                                      | Performance Impact                                                 |
|--------------------|-----------------------|-----------------------------|
| *Lowest* \$`r risk_item$COST_IMPACT_LOWEST`   | *Lowest* `r risk_item$SCHEDULE_IMPACT_LOWEST` days   | ***Performance Impact:*** `r risk_item$PERFORMANCEIMPACT_DESC`     |
| *Highest* \$`r risk_item$COST_IMPACT_HIGHEST` | *Highest* `r risk_item$SCHEDULE_IMPACT_HIGHEST` days | ***Performance Impact Type:*** `r risk_item$PERFORMANCEIMPACT` |
| `r risk_item$COST_IMPACT_EVIDENCE`            | `r risk_item$SCHEDULE_IMPACT_EVIDENCE`               | `r risk_item$PERFORMANCEIMPACT_DESC`                               |

| Cost Impact                                 | Schedule Impact                                    | Performance Impact                                             |
|---------------------|------------------------|---------------------------|
| *Lowest* \$`r risk_item$COST_IMPACT_LOWEST` | *Lowest* `r risk_item$SCHEDULE_IMPACT_LOWEST` days | ***Performance Impact:*** `r risk_item$PERFORMANCEIMPACT_DESC` |

#### **Point Estimate Example**

| Cost Impact                                      | Schedule Impact                                      | Performance Impact                                                                                                         |
|-------------------|-------------------|-----------------------------------|
| Most Likely `r risk_item$COST_IMPACT_MOSTLIKELY` | Most Likely `r risk_item$SCHEDULE_IMPACT_MOSTLIKELY` | ***Performance Impact:*** `r risk_item$PERFORMANCEIMPACT_DESC` Performance Impact Type: `r risk_item$PERFORMANCIMPACTTYPE` |
| `r risk_item$COST_IMPACT_EVIDENCE`               | `r risk_item$SCHEDULE_IMPACT_EVIDENCE`               | `r risk_item$PERFORMANCEIMPACT_DESC`                                                                                       |

#### Risk Treatments:

`r if(!treat_condit){"Risk treatments have not been completed for this risk item"}`

```{r echo=FALSE, message=FALSE, eval = treat_condit}
risk_treat_table$IMPLEMENT_IMG = sprintf("![    ](%s)", risk_treat_table$IMPLEMENT_IMG)


kbl(risk_treat_table,format = "html",col.names = NULL, align= "llccc") |>
  kable_styling() |>
  add_header_above(c("Measures"=2, "Impacts" = 2,"Implemented" = 1))


```

                                                
##### Risk Manager: `r risk_item$RISK_MANAGER` 

```{r echo=FALSE}
if (params$shinyrend)
  shiny::setProgress(.95)  # set progress to 95%
```

