---
output:
  html_document: default
  pdf_document: default
  always_allow_html: true
---

```{r, include=FALSE, echo=FALSE, warning = FALSE}
library(readr) 
library(magrittr) 
library(dplyr) 
library(kableExtra) 
library(rlang)
library(plotly)
library(ggplot2)
library(dplyr)
library(crosstalk)
library(tidyverse)
library(leaflet)
library(DT)
erisk_item <- read_csv("data/RiskItem_FullView_Update.csv")
risk_item_db<-data.frame(erisk_item)
erisk_project <- read_csv("data/RiskProject_FullView.csv")
risk_project_db<-data.frame(erisk_project)
risk_treat <- read_csv("data/RiskTreatment_FullView.csv")
imagepath<-"C:/workspace/e-rarr/images/check.png"

erisk_ItemProj<-left_join(risk_item_db, risk_project_db, by = "PROJECT_ID")

erisk_testing<-erisk_ItemProj[,c(3,5,6,8,22,27,32,40,51,56,64,65)]

RiskImpactTable<-erisk_ItemProj[,c(1,2,3,6,17,9,12,13,26,27,28,29,30,31,32,33,23,22,42,48,49,50,51,52)]


risk_item<-filter(RiskImpactTable, RiskImpactTable$RISK_ID == 7, RiskImpactTable$PROJECT_ID == 3069)
risk_treatment<-filter(risk_treat, risk_treat$PROJECT_ID == 3069, risk_treat$RISK_ID == 7)

risk_item_table<- risk_item %>%
  select(COST_IMPACT_LOWEST,COST_IMPACT_HIGHEST, COST_IMPACT_EVIDENCE,SCHEDULE_IMPACT_LOWEST, SCHEDULE_IMPACT_HIGHEST, SCHEDULE_IMPACT_EVIDENCE,PERFORMANCEIMPACT_DESC, PERFORMANCEIMPACTTYPE, PERFORMANCEIMPACT_DESC, SCHEDULE_IMPACT_DISTTYPE)


risk_treat_table<-risk_treatment %>%
  select(RISK_TREATMENT_ID,PROPOSED_RISK_TREATMENT,COST_IMPACT_RISK_TREATMENT,
         SCHEDULE_IMPACT_RISK_TREATMENT, IMPLEMENTED) %>%
  mutate(IMPLEMENT_IMG = case_when(
    IMPLEMENTED == 1 ~ imagepath,
    IMPLEMENTED == 0 ~ "")) %>%
  select(RISK_TREATMENT_ID,PROPOSED_RISK_TREATMENT,COST_IMPACT_RISK_TREATMENT,
         SCHEDULE_IMPACT_RISK_TREATMENT, IMPLEMENT_IMG)

    
```

# Risk Summary: `r risk_item$RISK_NAME`

```{r, milestoneplot, echo=FALSE, warning=FALSE, out.height= "10%" }
mockdf<- data.frame(ID = c("Project Initiation","Alternatives","Tentatively Selected Plan","Agency Decision","Senior Leaders Briefing","Chief's Report/Director's Report"),
                    yval = c(0,0,0,0,0,0),
                    xval = c(1,2,3,4,5,6))
mockdf$xwrap = str_wrap(mockdf$ID, width=10)

ggplot(mockdf, aes(x=ID, y=yval))+
  geom_segment(x=1, y = 0.15, xend = 6, yend = 0.15, size=1.5, color = "grey")+
  geom_point(size=8,color="grey", fill="snow1", shape=21, stroke=1.5)+
  geom_point(aes(x=risk_item$MILESTONE, y=0.15), colour="deepskyblue2", fill="deepskyblue2", shape = 21, size =8, stroke=1.5)+
  geom_text(aes(y=0.15,label=xwrap), vjust=1.7)+
  scale_y_continuous(expand=c(0,0))+
  theme(line = element_blank(),
        title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_blank(),
        panel.background = element_blank(), 
        plot.margin =unit(c(0,0,0,0), units="mm"))

ggplotly(mockplot, tooltip="x")
plot_ly(mockdf, x=mockdf$ID, y=mockdf$yval,type="scatter", mode = 'markers') %>%
  layout(xaxis=showgrid=F, yaxis= showgrid=F)

```

### Lead Discipline: `r risk_item$DISCIPLINE`

#### `r risk_item$RISK_STATEMENT`

## Event Likelihood: `r risk_item$LIKELIHOOD_DISC`

`r risk_item$PROB_OCCURRENCE_EVIDENCE`

| Cost Impact                                   | Schedule Impact                                      | Performance Impact                                                 |
|-----------------------------------------------|------------------------------------------------------|--------------------------------------------------------------------|
| *Lowest* \$`r risk_item$COST_IMPACT_LOWEST`   | *Lowest* `r risk_item$SCHEDULE_IMPACT_LOWEST` days   | ***Performance Impact:*** `r risk_item$PERFORMANCEIMPACT_DESC`     |
| *Highest* \$`r risk_item$COST_IMPACT_HIGHEST` | *Highest* `r risk_item$SCHEDULE_IMPACT_HIGHEST` days | ***Performance Impact Type:*** `r risk_item$PERFORMANCEIMPACTTYPE` |
| `r risk_item$COST_IMPACT_EVIDENCE`            | `r risk_item$SCHEDULE_IMPACT_EVIDENCE`               | `r risk_item$PERFORMANCEIMPACT_DESC`                               |

## Risk Treatments

```{r, echo=FALSE}
risk_treat_table$IMPLEMENT_IMG = sprintf("![](%s)", risk_treat_table$IMPLEMENT_IMG)
kbl(risk_treat_table,"html",col.names = NULL) %>%
  add_header_above(c("Measures"=2, "Impacts" = 2,"Implemented" = 1)) %>%
  kable_styling()


```

hi


